---
output:
  github_document
---


```{r}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(dplyr)
library(magrittr)
library(ggplot2)
library(tidyverse)
library(stringr)
library(readr)
library(expss)
library(data.table)
library(rsample)
library(caret)
library(modelr)
library(parallel)
library(foreach)

```

##Problem 1: ABIA
We mainly focus on the question: What is the best time of year to fly to minimize delays, and does this change by destination?
First, we calculate and plot the "Average Arrival delay in Different Month".
```{r}
ABIA = read.csv("data/ABIA.csv")
M1 = ABIA%>%
  na.omit()%>%
  group_by(Month) %>%
  summarise(delaymean = mean(ArrDelay))

ggplot(M1, aes(x = Month, y = delaymean)) + 
 scale_x_continuous(breaks = seq(1,12,1))+
 labs(x="Month of 2008",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Month")+
 geom_col()
```
From the plot, we can see that the Arrival delay time of Aguest, September and October is relatively lower than other month (lower than 50 minutes). Aguest is the lowest.

Then what about the different day of 2008? Will there be some trend?
```{r}
Q1 = ABIA %>%
  na.omit()%>%
  group_by(Month,DayofMonth) %>%
  summarise(delaymean = mean(ArrDelay))
Q1$DayofYear <- seq.int(nrow(Q1))
ggplot(Q1, aes(x = DayofYear, y = delaymean)) + 
 labs(x="Day of 2008",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Day")+
 geom_col()
```
```{r}
ggplot(Q2, aes(x = DayofMonth, y = delaymean)) + 
  facet_wrap(~Month)+
  labs(x="Day of Month",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Day/ Month")+

  geom_col()
```
There is no visible relationship of the delay time with different day but it seems that it has a seasonality. Let's check it.
```{r}
week = ABIA%>%
  na.omit()%>%
  group_by(DayOfWeek)%>%
  summarise(delaymean = mean(ArrDelay))

ggplot(week, aes(x = DayOfWeek, y = delaymean)) + 

 labs(x="Day of a Week",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Day of Week")+
 scale_x_continuous(breaks = seq(1,7,1))+
 geom_col()
```
We can see that Wednesday and Thursday have a relatively low average Arrival delay time.


##We can conclude that the best time of year to fly to minimize delays is Aguest, better to fly on Wednesday or Thursday.

##Check for different destination:
First count for the most frequently appeared destination (besides AUS)
```{r}
#frequency of dest
xa = xtabs(~Dest + Year, data=ABIA)

Freq = as.data.frame.matrix(xa)
data.frame(Dest = row.names(Freq),Freq,row.names = NULL,stringsAsFactors = FALSE)

freqmax = Freq%>%
  arrange(desc(`2008`))%>%
  head
show(freqmax)
```
Then we choose the most frequent three destination(above 5000 times): AUS, DAL and DFW to check

```{r}
#For AUS
Q3 = ABIA%>%
  filter(Dest == "AUS")%>%
  na.omit()%>%
  group_by(Month) %>%
  summarise(delaymean = mean(ArrDelay))

ggplot(Q3, aes(x = Month, y = delaymean)) + 
 scale_x_continuous(breaks = seq(1,12,1))+
 labs(x="Month of 2008",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Month")+
 geom_col()
```
For AUS, October has the smallest average Arrival delay time. Different from the overall situation.
```{r}
weekaus = ABIA%>%
  filter(Dest == "AUS")%>%
  na.omit()%>%
  group_by(DayOfWeek)%>%
  summarise(delaymean = mean(ArrDelay))

ggplot(weekaus, aes(x = DayOfWeek, y = delaymean)) + 

 labs(x="Day of a Week",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Day of Week")+
 scale_x_continuous(breaks = seq(1,7,1))+
 geom_col()
```
For AUS, roughly same as the overall situation.

```{r}
Q4 = ABIA%>%
  filter(Dest == "DAL")%>%
  na.omit()%>%
  group_by(Month) %>%
  summarise(delaymean = mean(ArrDelay))

ggplot(Q4, aes(x = Month, y = delaymean)) + 
 scale_x_continuous(breaks = seq(1,12,1))+
 labs(x="Month of 2008",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Month")+
 geom_col()
```
For DAL, Aguest has the lowest average Arrival delay time, same as the overall situation.
```{r}
weekdal = ABIA%>%
  filter(Dest == "DAL")%>%
  na.omit()%>%
  group_by(DayOfWeek)%>%
  summarise(delaymean = mean(ArrDelay))

ggplot(weekdal, aes(x = DayOfWeek, y = delaymean)) + 

 labs(x="Day of a Week",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Day of Week")+
 scale_x_continuous(breaks = seq(1,7,1))+
 geom_col()
```
For DAL, Monday has the lowest average arrival delay time, different from the overall situation.

```{r}
Q5 = ABIA%>%
  filter(Dest == "DFW")%>%
  na.omit()%>%
  group_by(Month) %>%
  summarise(delaymean = mean(ArrDelay))

ggplot(Q5, aes(x = Month, y = delaymean)) + 
 scale_x_continuous(breaks = seq(1,12,1))+
 labs(x="Month of 2008",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Month")+
 geom_col()
```
For DFW, October has the smallest average Arrival delay time. Different from the overall situation.
```{r}
weekdfw = ABIA%>%
  filter(Dest == "DFW")%>%
  na.omit()%>%
  group_by(DayOfWeek)%>%
  summarise(delaymean = mean(ArrDelay))

ggplot(weekdfw, aes(x = DayOfWeek, y = delaymean)) + 

 labs(x="Day of a Week",y="Average Arrival Delay Time by Minutes",title="Average Arrival delay in Different Day of Week")+
 scale_x_continuous(breaks = seq(1,7,1))+
 geom_col()
```
For DFW, Wednesday has the lowest average arrival delay time, roughly same as the overall situation.

##The best time of year/week changes by destination.


##Problem 2: Olympic
A)
```{r}
olympics_top20 = read.csv("data/olympics_top20.csv")
F_height = olympics_top20%>% 
  na.omit()%>%
  filter(sex== "F" & sport=="Athletics")%>%
  group_by (id)
  quantile(F_height$height, probs = c(0.95))
```
B)
```{r}
Var_h = olympics_top20%>%
  filter(sex=="F")%>%
  group_by (event)%>%
  summarise(mean_h = mean(height),sd_h = sd(height))%>%
  arrange(desc(sd_h))%>%
  head(10)%>%
  show()
```
For single women's event, "Swimming Women's 100 metres Butterfly" had the greatest variability in competitor's heights across the entire history of the Olympics, as measured by the standard deviation.

C)
```{r}
swim_age = olympics_top20%>%
  filter(sport == "Swimming")%>%
  group_by(year)%>%

  summarise(mean_age = mean(age))
ggplot(swim_age, aes(x = year, y = mean_age)) + 
  scale_x_continuous(breaks = seq(1896,2016,8))+

 geom_line()
```
The trend

```{r}
swimage1 = olympics_top20%>%
  filter(sport == "Swimming")%>%
  group_by(year,sex)%>%
  summarise(mean_age1 = mean(age))  
ggplot(swimage1, aes(x = year, y = mean_age1, color = sex)) + 
  scale_x_continuous(breaks = seq(1896,2016,8))+
  geom_line()+
  labs(title="The Average Age of Women and Men Swimmers",
       y="average age",
       x = "year") 
```
The


Problem 3: sclass
For trim = 350
```{r}

sclass = read.csv("data/sclass.csv")
car_350 = sclass %>%
  filter(trim == '350')
summary(car_350)
# plot the data
ggplot(data = car_350) + 
  geom_point(mapping = aes(x = mileage, y = price), color='darkgrey')
# split
car_350_split = initial_split(car_350, prop=0.8)
car_350_train = training(car_350_split)
car_350_test  = testing(car_350_split)
k_grid = c(2, 4, 6, 8, 10, 15, 20, 25, 30, 35, 40, 45,
           50, 60, 70, 80, 90, 100, 125, 150, 175, 200, 250, 300)
rmse_out = foreach(i=1:20, .combine='rbind') %dopar% {
  
  this_rmse = foreach(k = k_grid, .combine='c') %do% {

    knn_model = knnreg(price ~ mileage, data=car_350_train, k = k, use.all=TRUE)
    modelr::rmse(knn_model, car_350_test)
  }
  data.frame(k=k_grid, rmse=this_rmse)
}
rmse_out = arrange(rmse_out, k)
ggplot(rmse_out) + geom_point(aes(x=factor(k), y=rmse)) + theme_bw(base_size=7)

```
We can see that the bottom is k = 15.

```{r}
knn = knnreg(price ~ mileage, data=car_350_train, k=15)
car_350_test = car_350_test %>%
  mutate(price_350_pred = predict(knn, car_350_test))
pred_350_test = ggplot(data = car_350_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)

pred_350_test + geom_line(aes(x = mileage, y = price_350_pred), color='red', size=1.5)

```
For Trim = 65 AGM
```{r}
car_65 = sclass %>%
  filter(trim == '65 AMG')
summary(car_65)
# plot the data
ggplot(data = car_65) + 
  geom_point(mapping = aes(x = mileage, y = price), color='darkgrey')
# split
car_65_split = initial_split(car_65, prop=0.8)
car_65_train = training(car_65_split)
car_65_test  = testing(car_65_split)
k_grid = c(2, 4, 6, 8, 10, 15, 20, 25, 30, 35, 40, 45,
           50, 60, 70, 80, 90, 100, 125, 150, 175, 200, 250, 300)
rmse_out = foreach(i=1:20, .combine='rbind') %dopar% {
  
  this_rmse = foreach(k = k_grid, .combine='c') %do% {

    knn_model = knnreg(price ~ mileage, data=car_65_train, k = k, use.all=TRUE)
    modelr::rmse(knn_model, car_65_test)
  }
  data.frame(k=k_grid, rmse=this_rmse)
}
rmse_out = arrange(rmse_out, k)
ggplot(rmse_out) + geom_point(aes(x=factor(k), y=rmse)) + theme_bw(base_size=7)
```
We can see that the bottom is k = 10.

```{r}
knn = knnreg(price ~ mileage, data=car_65_train, k=10)
car_65_test = car_65_test %>%
  mutate(price_65_pred = predict(knn, car_65_test))
pred_65_test = ggplot(data = car_65_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)

pred_65_test + geom_line(aes(x = mileage, y = price_65_pred), color='red', size=1.5)
```




